Risk Perceptions for Wearable Devices

### 2015-03-05 tex-inputs/results-regression.tex
Added coding descriptions

After independently coding all data types with respect to these categories, the researchers met to resolve any disagreements, such that the resulting codings reflected unanimity. Prior to this resolution, there was  83\% agreement. Cohen's $\kappa$ was 0.81 for the data categories and 0.75 for the associated risks, both indicating ``excellent'' agreement~\cite{Fleiss2003}.

@@

Using these two new variables as additional independent variables (and removing the previous data type variable), we created a second set of models. Because these risk categories and mediums are less likely to change over time, models that take these into account are likely to be more useful and less likely to be overfit. What these models show us is that both risk and medium are relatively strong predictors by themselves, and have an even stronger interaction effect. When the data recipient and covariates are added to the model, the resulting goodness-of-fit is not much worse than that of the model using the actual data type.

>>>>

After independently coding all data types with respect to these categories, the researchers met to resolve any disagreements, such that the resulting codings reflected unanimity. Prior to this resolution, there was  83\% agreement. Cohen's $\kappa$ was 0.81 for the data categories and 0.75 for the associated risks, both indicating ``excellent'' agreement~\cite{Fleiss2003}. Applying this taxonomy to our collected data, we observed that average VURs were highest for financial risks (82.0\%) and lowest for medical data risks (47.4\%). In the middle were relationships (69.2\%), physical (66.4\%), and self-image (65.8\%) risks. One reason why medical risks were ranked relatively low is that this may be a misnomer: in addition to covering scenarios involving data about the user's health, it also covered basic demographics, such as age, gender, and emotional state. Similar to what we observed in Section \ref{sec:datatypes}, participants likely understood that many of these data types are publicly observable, which is why they were less concerned.

With regard to the VURs of the broad categories of data that we coded, the most concerning type of data was video (78.0\%), which was ranked similarly to photos (76.2\%). Next were audio (66.8\%) and demographic data (65.4\%), followed by behavioral (53.1\%) and biometric (46.3\%) data. In this case, we suspect that demographic data was more concerning than we expected because it included information that could be used to perpetuate fraud or identity theft, such as a Social Security Number, bank account information, and other financial information. We were very surprised that biometric information was seen as relatively benign (at least as compared to the other broad categories of data). One hypothesis is that since most home users do not use biometric authentication, they may have a poorer understanding of the types of systems that might be at risk if biometric data were to be stolen and then abused.

@@

Using these two new variables as additional independent variables (and removing the previous data type variable), we created a second set of models. Because these risk categories and mediums are less likely to change over time, models that take these into account are likely to be more useful and less likely to be overfit. What these models show us is that both risk and medium are relatively strong predictors by themselves, and have an even stronger interaction effect. When the data recipient and covariates are added to the model, the resulting goodness-of-fit is not much worse than that of the model using the actual data type. The full model can be found in Appendix \ref{sec:regression2}.
